Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch

### 2017-02-25 netsoft_paper.tex
cite frank's paper

\subsection{Overall procedure of application identification}
In order to let QoS management system be able to control or distribute bandwidth at application level, we designed and implemented an application identification system (also called flow classification system) to judge each flow is established by what application. In other words, the application identification system can classify each flow as an application name in real time, rather than a rough category or a transport layer protocol. The corresponding application name of a flow means the name of the application which establishes the flow. We use supervised machine learning (ML) and a method based on inspecting domain name service (DNS) responses to do flow classification. The system analyzes the packets whose transport protocol are TCP or UDP. Except for DNS responses, the system only reads headers to get transport layer information of packets without inspecting their payload.

\subsection{Procedure of Supervised ML in our system}
In training phase, the architecture is show in Fig. \ref{fig:class_training}. Flow classification engine is to build classification model by training data from Trainer, and update the model when new training data comes. Trainer is to analyze traffic from mirror port to get flow attributes. After Trainer finishes calculating flow attributes of a flow, it gets ground truth of the flow from Scanner or App Meta Server to generate training data, and sends training data to flow classification engine. App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer. Scanner is to get mappings of 5-tuple and ground truth from OS.
In classifying phase, the architecture is shown in Fig. \ref{fig:class_classifying}. Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result, and sends classification result to Classifier. Classifier is to analyze traffic from mirror port to get flow attributes. After Classifier finishes calculating flow attributes of a flow, it use flow attributes to ask flow classification engine for classification result if needed.

@@

\subsection{Algorithms we adopted in supervised ML}
We use algorithms implemented by Weka, a famous open source ML tool developed at the University of Waikato. We call Weka Java API to build classification model. We use three algorithms, namely RandomSupSpace with RandomTree, FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.

@@

\subsubsection{Accuracy matrices and results}
To evaluate accuracy, we used precision, recall and F-measure (also called F1 score), as shown in Eq. (1), Eq. (2), and Eq. (3) []. In each round in 10-fold cross validation, we calculate precision and recall of each category to calculate F1 score of each category. After ten rounds, we calculate average F1 score of each category in 10 rounds. Table I shows F1 score of each category in top 40 most popular applications in testing data set. Next, we calculate average F1 score of all categories in 10 rounds, and we get 0.9062. The result (Table. \ref{table:classification_result}) shows it achieved high accuracy, which makes QoS possible to do bandwidth control or distribution at application level.

>>>>

\subsection{Overall procedure of application identification}
In training phase, we generate some data needed by our proposed method.
In classifying phase, if a flow meet some requirement, we use the method based on inspecting DNS response to classify;
otherwise, we use supervised ML to classify.

\subsection{Procedure of Supervised ML in our system}
In training phase, the architecture is show in Fig. \ref{fig:class_training}.
Flow classification engine is to build classification model by training data from Trainer,
and update the model when new training data comes.
Trainer is to analyze traffic from mirror port to get flow attributes.
After Trainer finishes calculating flow attributes of a flow,
it gets ground truth of the flow from Scanner or App Meta Server to generate training data\cite{Iwai2016},
and sends training data to flow classification engine.
App Meta Server is to store mappings of 5-tuple and ground truth from Scanner, and accept queries from Trainer.
Scanner is to get mappings of 5-tuple and ground truth from OS\cite{app-awareness-sdn}.
In classifying phase, the architecture is shown in Fig. \ref{fig:class_classifying}.
Flow classification engine is to use flow attributes from Classifier and classification model to get a classification result,
and sends classification result to Classifier.
Classifier is to analyze traffic from mirror port to get flow attributes.
After Classifier finishes calculating flow attributes of a flow,
it use flow attributes to ask flow classification engine for classification result if needed.

@@

\subsection{Algorithms we adopted in supervised ML}
We use algorithms implemented by Weka, a famous open source ML tool developed at the University of Waikato.
We call Weka Java API to build classification model.
We use three algorithms, namely RandomSupSpace with RandomTree\cite{TinKamHo1998},
FilterClassifier with discretization and RandomTree, and RandomCommittee with RandomTree.

@@

\subsubsection{Accuracy matrices and results}
To evaluate accuracy, we used precision, recall and F-measure (also called F1 score),
as shown in Eq. (1), Eq. (2), and Eq. (3) \cite{muc4}. In each round in 10-fold cross validation,
we calculate precision and recall of each category to calculate F1 score of each category.
After ten rounds, we calculate average F1 score of each category in 10 rounds. Table I shows F1 score of each category in top 40 most popular applications in testing data set. Next, we calculate average F1 score of all categories in 10 rounds, and we get 0.9062. The result (Table. \ref{table:classification_result}) shows it achieved high accuracy, which makes QoS possible to do bandwidth control or distribution at application level.
